Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-26 paper.tex
redid fake message calculations and added graphs

\section{Design overview}
TODO: turn this into real words.

encrypt, hiding sender information inside the contents, inside a special folder. index, lock messages to handle multiple clients. hide metadata by using a combination of scheduling, mixing, fake decoy messages, and possibly ORAM-like techniques. rollback detection for index and messages. key is passphrase/scrypt kdf with salt.

@@

The requirements that \project has for operations on messages bear resemblance to those of memory operations in oblivious random access memory (ORAM)\cite{oram}. ORAM assumes a situation where multiple actors (say CPUs) can see memory access and store actions on a shared memory module. It proposes a system of additional memory accesses and locations to shield patterns of which memory locations have been accessed. ORAM techniques and implementations are an active area of research, some with proven lower bounds on additional bandwidth cost \cite{stefanov2013path}.

@@

If we wish the growth rate of the server to precisely match the rate of messages to be pushed, we must perform many mixing operations. Intuitively, this is because to grow with the actual rate, each fake message that was in an UP operation must appear in a DOWN operation. Mathematically, assume that the mailbox is seeded with $k-1$ fake messages. Consider again messages R and F, and call MIX NUMBER $m$. This time, R and F were each one of $m + 1$ messages pushed to the server, with R pushed into set A and F pushed into set B. Assume no overlap between A and B, since $m<<n$, the total number of messages. This case is similar to the case of no extraneous growth without mixing assessed above, since we are extremely unlikely to have chosen a message in set B were one of them not fake. More precisely, we have at least a $1/k$ probability of choosing a messaging from set B. For choosing at least one message from set A, though, we have a probability of $q = \frac{{m \choose 1}{n-1 \choose m-1}}{{n \choose m}}$. We have ${n \choose k}$ possible ways of choosing $m$ messages from all $n$, and out of those, if at least one must be in A with size $m$, there are ${m \choose 1}$ ways of choosing from those $m$, with any message of the remaining $n-1$ allowed for the remaining $m-1$ spots. We can simplify $q$ to $\frac{m^2}{n}$.

For a reasonable estimation, assume $n=5000$ and $m=10$. Then, $k$ must be at least 50. But this analysis only applies if the adversary does not know which of the messages are the fake $k$ at every time step. So, how many mixing operations do we require to completely mix all $n$ messages? If we are selecting at random, this is the expected number of operations required to select all $n$ messages in batches of $m$, which is a variation on the coupon collector problem. It is not precisely the coupon collector problem, since we are selecting ten at a time, and therefore one batch cannot contain duplicates of the same message, so there is a slightly higher probability of selecting a new one for later messages in a batch. Thus, we can place a lower bound on the number of mixing operations required to select $n$ messages at $E(n) = n \ln (n) / m$. Using our estimates of $5000$ and 10, this is over 4000 mixing operations. We must pull down and push up a total of $2m$ messages for each operation, so that is $2n\ln (n)$ messages that must be transferred to entirely mix the mailbox regardless of $m$. This is unreasonable to do on a regular basis.

@@

TODO: make graphs showing these tradeoffs

@@

TODO: deal with the problem of making a fetch-delete-append operation indistinguishable from an append operation in the way that ORAM get and reads are indistinguishable.

>>>>

\section{Design overview}
To meet these requirements, we present \projectnospace, a client-only extension to the IMAP protocol that provides metadata privacy-preserving storage for multiple \project clients. In \projectnospace, emails received at the client are fully encrypted, including mail headers, indexed, and uploaded to a specialized folder in the IMAP server. This hides sender and recipient information from the IMAP server. Encryption is based on a passphrase and generated salt, using scrypt as a key derivation function. A special-use index message is stored in the folder as well, and tracks metadata for the client such as the apparent folder that a message is in (visible only to clients, not the server). A special-use lock message is used to allow multiple clients access to the same folder, in keeping with IMAP's design principles. Message arrival times are hidden from the server using a combination of scheduling, mixing, fake decoy messages, and techniques drawn from oblivious RAM. \project provides rollback detection for both messages and the index, using version numbers saved client-side and message hashes stored server-side. It is robust to client failure in any state.

@@

The requirements that \project has for operations on messages bear resemblance to those of memory operations in oblivious random access memory (ORAM)\cite{oram}. ORAM assumes a situation where multiple actors (say CPUs) can see memory access and store actions on a shared memory module. It proposes a system of additional memory accesses and locations to shield patterns of which memory locations have been accessed, making read and write operations indistinguishable from each other. ORAM techniques and implementations are an active area of research, some with proven lower bounds on additional bandwidth cost \cite{stefanov2013path}.

@@

If we wish the growth rate of the server to precisely match the rate of messages to be pushed, we must perform many mixing operations. Intuitively, this is because to grow with the actual rate, each fake message that was in an UP operation must appear in a DOWN operation. Mathematically, assume that the mailbox is seeded with $k-1$ fake messages. Consider again messages R and F, and call MIX NUMBER $m$. This time, R and F were each one of $m + 1$ messages pushed to the server, with R pushed into set A and F pushed into set B. Assume no overlap between A and B, since $m<<n$, the total number of messages. This case is similar to the case of no extraneous growth without mixing assessed above, since we are extremely unlikely to have chosen a message in set B were one of them not fake. More precisely, we have at least a $1/k$ probability of choosing a messaging from set B. For choosing at least one message from set A, though, we have a probability equivalent to $1-$ the probability of choosing 0 messages from set A. This is equivalent to choosing all $m$ messages from the $n-m$ messages not in set A, which there are ${{n-m}\choose m}$ ways to do. This gives a probability of choosing at least one message of the $m$ chosen messages from set A of $1-\frac{{{n-m}\choose m}}{{n \choose m}}$.

For a reasonable estimation, assume $n=5000$ and $m=10$, which gives a probability of choosing from set A of slightly under 0.02. Then, $k$ must be at least 50 to give equivalent probabilities for choosing from sets A and B. But this analysis only applies if the adversary does not know which of the messages are the fake $k$ at every time step. So, how many mixing operations do we require to completely mix all $n$ messages? If we are selecting at random, this is the expected number of operations required to select all $n$ messages in batches of $m$, which is a variation on the coupon collector problem. It is not precisely the coupon collector problem, since we are selecting ten at a time, and therefore one batch cannot contain duplicates of the same message, so there is a slightly higher probability of selecting a new one for later messages in a batch. Thus, we can place a lower bound on the number of mixing operations required to select $n$ messages at $E(n) = n \ln (n) / m$. Using our estimates of $5000$ and 10, this is over 4000 mixing operations. We must pull down and push up a total of $2m$ messages for each operation, so that is $2n\ln (n)$ messages that must be transferred to entirely mix the mailbox regardless of $m$. This is unreasonable to do on a regular basis.

@@

The following graphs shows the expected number of mixes before including a fake message in a batch as $n$ increases given different batch sizes $m$, for various functions of $n$. To calculate them, we find the expected number of mixes before encountering a fake message, if each mix has a probability $p$ of including at least one fake message, which since mixes have independent probability of encountering a fake message is $1/p$. To calculate $p$, we consider that we are choosing $m$ messages from a total size of $n$, and we would like the probability of selecting at least one fake message given that there are $k=f(n)$ fake messages. This is equivalent to $1-$ the probability of choosing 0 fake messages, which is $\frac{{{n-k}\choose m}}{{n \choose m}}$.

\includegraphics[width=\textwidth]{lgn}

Using the logarithm base 2 of $n$ grows too slowly relative to $n$ to have sufficient saturation.

\includegraphics[width=\textwidth]{sqrtn}

With high bandwidth, including only $\sqrt(n)$ fake messages could be feasible: with a batch size of 16, even at a total mailbox size of 5000 we would still encounter a fake message about every 5 mixes.

\includegraphics[width=\textwidth]{nover2}

With a linear function where half the mailbox is composed of fake messages, we achieve spectacular rates of message inclusion, of course, but we waste much space in the mailbox.

\includegraphics[width=\textwidth]{nover10}

Changing the constant on our linear function, we can save substantial mailbox space while still achieving very reasonble delays. With only one tenth of messages being decoy messages, we will encounter a fake message about every 3 mixes with a batch size of only 4, and just over every 1.5 mixes with a batch size of 8.

@@

While most ORAM abstractions map trivially onto IMAP operations, a significant difference is that most ORAM techniques are constructed for a fixed-size store. A trivial way to handle this is to initially seed the mailbox to near-full capacity, and disallow emails to arrive from legacy pathways. We can do better though, using Resizable Tree-Based ORAM as described in \cite{moatazresizable}. This protocol provides alloc and free operations in addition to read/write, in a way that leaks only the current number of elements, and is thus the appropriate construction for the abstractions of an IMAP-like system.
